---
title: "196_R"
author: "Tyler Kim"
date: "11/1/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(error=TRUE)
```

### R Markdown and Basic R

The assignment should be all written in RMarkdown (.rmd) and knitted to a HTML file.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. 


You can embed an R code chunk like this:


```{r cars}
summary(cars)
```

#### Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

### Let's add some steroid. 

For this, we will use the `faithful` dataset. This is a default dataset in `R`, so there is no need to load it. You should use `?faithful` to learn about the background of this dataset.

Suppose we would like to predict the duration of an eruption of [the Old Faithful geyser](http://www.yellowstonepark.com/about-old-faithful/) in [Yellowstone National Park](https://en.wikipedia.org/wiki/Yellowstone_National_Park) based on the waiting time before an eruption.

Let's fit a simple linear model in `R` that accomplishes this task. We will store the results in a variable called `faithful_model`. 

```{r}
faithful_model = lm(eruptions ~ waiting, data=faithful)
summary(faithful_model)

```

Let's output only the estimated regression coefficients. We will interpret $\beta_0$ and $\hat{\beta_1}$ in the *context of the problem*. 

```{r}
coef(faithful_model)
```

Let's use our model to predict the duration of an eruption based on a waiting time of **80** minutes. 

```{r}
range(range(faithful$waiting))
```

```{r}
predict(faithful_model, data.frame(waiting = 80))
```

```{r}
predict(faithful_model, data.frame(waiting = 120))
```

Calculating the RSS for this model.
```{r}
sum(resid(faithful_model)^2)
```

Let's create a scatterplot of the data and add the fitted regression line. Make sure your plot is well labeled and is somewhat visually appealing.

```{r}
plot(eruptions ~ waiting, data=faithful,
     xlab = "Waiting Time (mins)",
     ylab = "Eruptions Length (mins)",
     main = "Eruption Leanth vs. Waiting Time",
     pch = 18,
     cex = 1,
     col = "red")
abline(faithful_model, col = "blue")
```


## Challenge 1
This section contains many “errors” that appear in R code. Your job is to solve them and explain how you fixed the problem.

```{r}
#1
f = function(x){
  n = a+x
}

f(1)

```

```{r}
#2
p = function(x){
  log(p/(1-p))
}

vals = seq(0, 1, by = 0.1)

p(vals)

```

```{r}
#3
d = c(1, 3, NA, 5, 6, 9)

mean(d) == 1/length(d)*sum(d)

```

```{r}
#4
set.seed(145)

d = sample(1:10, 5)
b = sample(1:10, 5)

if(d > b){
  d + 5
}
else {
  b * 2
}

```

```{r}
#5
set.seed(1234)

f = function() {
    if (runif(1) > .8) stop("oops")
    TRUE
}

g = function() {
  tryCatch(f(),
           error = function(err) { warning(conditionMessage(err)) }
           )
}

a = replicate(10, g())
if(is.logical(a) && sum(a) > 0){
  cat("We had a few successes!\n")
}

```

## Challenge 2

RMarkDown is important.

You can literally do Web-Dev in RMarkdown and RMarkdown only!


You can literally do Web-Dev in RMarkdown and RMarkdown only!

##### Round 1
- Download the html for http://xkcd.com/
- Extract the URL for the daily comic.
- Download the comic image to disk.
  - Include the Comic picture inside the R Markdown file.
  - If I appreciate the comic, I might grade easily?

##### Round 2  (optional & for extra credit /s)
- Establish an ```html_session``` with ```rvest``` pointed at https://slashdot.org/.
  - You are only allowed to hardcode https://slashdot.org/
- Navigate to the Science news section of slashdot given at


https://science.slashdot.org/ by having ```rvest``` click the appropriate link. - Scrap all of the titles of the articles on the first and second pages. - Provide the selector information that you used. - Scrap all the URLs given within each of the story descriptions. - Provide the selector information that you used. - List the URLs next to the Titles. - You can embed a ```list``` with the titles inside a data.frame!

## Challenge 3.

Let's refer back to Week4's challenge. We are going to - whoops, I meant - you guys will be doing the Week 4 Challenges in R!


Here are the links to the Week 4 Challenge + the raw date source
https://github.com/CS196Illinois/Data_Hackerspace/blob/master/week4/NumpyAndPandas.ipynb
https://raw.githubusercontent.com/mwaskom/seaborn-data/master/titanic.csv


###### 1. Calculate the survival rates of passengers by class (First, Second, Third)


###### 2. Calculate the average fare paid by those who survived compared to the fare paid by those who didn't


###### 3. Plot the ages of the female survivors that embarked at Cherbourg
